IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-04 ms.tex
I added a quick figure of simple Mie scattering curve fits.
I added some explanations of the Mie fits.

@@

\begin{abstract}
BD Science
\end{abstract}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:specphot}
\end{figure*}

@@

\section{Conclusions}

>>>>

%This is a test by Gizis

@@

\begin{abstract}
L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres. We present a high precision ground-based study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010. 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m. 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m. We interpret the spectral variability in 2MASS J1821 as being due to clouds with sub-micron-sized particles.
\end{abstract}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

\section{Simple Model Fits}

We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
We model the extinction coefficient from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains.
For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
\section{Conclusions}
